Inference for multivariate peaks over threshold models

### 2021-11-17 abstract.tex
updates

{\bf We need an abstract}
Extreme analysis

Drawing on the constructive definition for the multivariate Pareto introduced in~\cite{ferreira2014} which separates the radial component of the RV from the angular, we introduce a method for inferring the distribution of the angular component.

>>>>

{\bf We need an abstract}

The constructive definition of the multivariate Pareto separates the Pareto RV into
    a radial component, following a univariate Pareto distribution, and independently
    an angular component, defined on the surface of the positive orthant of the unit 
    hypercube.  In this paper, we 
    propose a method for inferring the distribution of that angular component.  We  
    identify its support as the limit of the unit $p$--norm
    spheres, and describe a means by which we project a distribution onto those spheres.
    We then introduce a family of \emph{projected Gamma} distributions, defined by the
    power of the unit norm sphere on which they have support.  This projected Gamma family
    serves as a building block to a Dirichlet process mixture of projected Gammas model,
    which we ultimately present.

We discuss model scoring methods appropriate to this space, and develop a kernel metric
    to be used with the \emph{energy score} criterion for evaluating models.  We compare
    these results with those obtained using the posterior predictive loss criterion.  
    We compute model scores
    on various iterations of the aforementioned model, fitted to simulated data.  We then
    apply the model to the \emph{integrated vapor transport} (IVT)---a dataset describing 
    the quantity of water vapor in the atmosphere, used for identifying atmospheric 
    rivers---to demonstrate the model on \emph{real} data.

% EOF
